The Rising Return to Non Cognitive Skill

### 2023-02-17 Outputs/Paper/paper.qmd
updated graphs a bit

sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  labs(
    title = "Sum of All Bullying",
    x = "School Year Date Intervals",
    y = "Sum of Searches by Investigated States"
  )
sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  labs(
    title = "Sum of Cyberbullying",
    x = "School Year Date Intervals",
    y = "Sum of Searches by Investigated States"
  )
sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  labs(
    title = "Sum of School Bullying",
    x = "School Year Date Intervals",
    y = "Sum of Searches by Investigated States"
  )

>>>>

sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black")) +
  labs(
    title = "All 'Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Total Searches"
  )
sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black")) +
  labs(
    title = "'Cyberbullying' Searches in High Asian Population States",
    x = "Date",
    y = "Total Searches"
  )
sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black")) +
  labs(
    title = "'School Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Total Searches"
  )
